---
title: "Open_Interest"
author: "Jacob Gipson"
date: '2022-10-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Load Packages and Data
```{r}
library(tswge)
library(tseries)
library(nnfor)
oi = read.csv("/Users/jacobgipson/Documents/SMU/Capstone/OpenInterestData.csv",header = T)
oi.train = oi[1:384,]
oi.test = oi[385:434,]
```

#### Initial SPY plot
```{r}
spy.train = oi.train$SPX.Open.Interest
plotts.sample.wge(spy.train, lag.max = 100)
adf.test(spy.train)
par(mfrow = c(1,1))
plotts.wge(spy.train)
acf(spy.train, lag.max = 100)
parzen.wge(spy.train)
```
##### Initial Thoughts
###### Series does not seem stationary, but has constant variance for  the most part
###### ACF plot shows weird pattern
###### Parzen window shows a peak at 0. 

```{r}
spy.d1 = artrans.wge(spy.train, phi.tr = 1)
plotts.sample.wge(spy.d1, arlimits = T)
#aic5.wge(spy.d1, p = 0:10, q = 0:10)
#aic5.wge(spy.d1, p = 0:10, q = 0:10, type = "bic")
```
#### Differencing seems to take out much of the sample correlations
#### We also get a stationary time sereis, there is concern regarding variance but it only seems that way at one point
#### Upon review, that point happens somewhere in June/July 2022, so I'm not sure how to explain that
#### AIC/BIC favors (1,1), (4,1), and (3,2) after differencing
#### Next we will estimate the parameters and check MSE to see which performs best
```{r}
spy11 = est.arma.wge(spy.d1, p = 1, q = 1)
spy41 = est.arma.wge(spy.d1, p = 4, q = 1)
spy32 = est.arma.wge(spy.d1, p = 3, q = 2)
```
```{r}
spy.test = oi.test$SPX.Open.Interest

spy11f = fore.arima.wge(spy.train, phi = spy11$phi, theta = spy11$theta, d = 1, n.ahead = 50)
spy41f = fore.arima.wge(spy.train, phi = spy41$phi, theta = spy41$theta, d = 1, n.ahead = 50)
spy32f = fore.arima.wge(spy.train, phi = spy32$phi, theta = spy32$theta, d = 1, n.ahead = 50)


spy11ASE_5 = mean((spy11f$f[1:5]-spy.test[1:5])^2)
spy41ASE_5 = mean((spy41f$f[1:5]-spy.test[1:5])^2)
spy32ASE_5 = mean((spy32f$f[1:5]-spy.test[1:5])^2)

spy11ASE_10 = mean((spy11f$f[1:10]-spy.test[1:10])^2)
spy41ASE_10 = mean((spy41f$f[1:10]-spy.test[1:10])^2)
spy32ASE_10 = mean((spy32f$f[1:10]-spy.test[1:10])^2)

spy11ASE = mean((spy11f$f-spy.test)^2)
spy41ASE = mean((spy41f$f-spy.test)^2)
spy32ASE = mean((spy32f$f-spy.test)^2)

spy11ASE_5
spy41ASE_5
spy32ASE_5

spy11ASE_10
spy41ASE_10
spy32ASE_10

spy11ASE
spy41ASE
spy32ASE
```
#### By ASE ARIMA(3,1,2) looks the best but I am not convinced.
```{r}
plotts.sample.wge(spy32$res, arlimits = T)
ljungbox32 = ljung.wge(spy32$res, p = 3, q = 2)
ljungbox32.48 = ljung.wge(spy32$res, p = 3, q = 2, K = 48)

plotts.sample.wge(spy11$res, arlimits = T)
ljungbox11 = ljung.wge(spy11$res, p = 1, q = 1)
ljungbox11.48 = ljung.wge(spy11$res, p = 1, q = 1, K = 48)

plotts.sample.wge(spy41$res, arlimits = T)
ljungbox41 = ljung.wge(spy41$res, p = 1, q = 1)
ljungbox41.48 = ljung.wge(spy41$res, p = 1, q = 1, K = 48)
```
```{r}
ljungbox32$pval
ljungbox32.48$pval
ljungbox11$pval
ljungbox11.48$pval
ljungbox41$pval
ljungbox41.48$pval
```
#### Fails to reject- so does not show  a lack of fit

#### Lets assume a stationary model
```{r}
plotts.sample.wge(spy.train, arlimits = T)
#aic5.wge(spy.train, p = 0:10, q = 0:10)
#aic5.wge(spy.train, p = 0:10, q = 0:10, type = "bic")
par(mfrow = c(1,1))
plotts.wge(spy.train)
```
#### We will look at (2,0), (1,1), (1,2)
```{r}
spy1.1 = est.arma.wge(spy.train, p = 1, q = 1)
spy1.2 = est.arma.wge(spy.train, p = 1, q = 2)
spy2.0 = est.ar.wge(spy.train, p = 2, method = "burg")
```
```{r}
spy1.1f = fore.arma.wge(spy.train, phi = spy1.1$phi, theta = spy1.1$theta, n.ahead = 50)
spy1.2f = fore.arma.wge(spy.train, phi = spy1.2$phi, theta = spy1.2$theta, n.ahead = 50)
spy2.0f = fore.arma.wge(spy.train, phi = spy2.0$phi, theta = 0, n.ahead = 50)

spy1.1ASE_5 = mean((spy1.1f$f[1:5]-spy.test[1:5])^2)
spy1.2ASE_5 = mean((spy1.2f$f[1:5]-spy.test[1:5])^2)
spy2.0ASE_5 = mean((spy2.0f$f[1:5]-spy.test[1:5])^2)

spy1.1ASE_10 = mean((spy1.1f$f[1:10]-spy.test[1:10])^2)
spy1.2ASE_10 = mean((spy1.2f$f[1:10]-spy.test[1:10])^2)
spy2.0ASE_10 = mean((spy2.0f$f[1:10]-spy.test[1:10])^2)

spy1.1ASE = mean((spy1.1f$f-spy.test)^2)
spy1.2ASE = mean((spy1.2f$f-spy.test)^2)
spy2.0ASE = mean((spy2.0f$f-spy.test)^2)

spy1.1ASE_5
spy1.2ASE_5
spy2.0ASE_5

spy1.1ASE_10
spy1.2ASE_10
spy2.0ASE_10

spy1.1ASE
spy1.2ASE
spy2.0ASE
```
```{r}
plot(spy.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$SPX ARMA(1,1) 5-Day Forecast")
lines(seq(1,5),spy1.1f$f[1:5],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)

plot(spy.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$SPX ARMA(1,1) 10-Day Forecast")
lines(seq(1,10),spy1.1f$f[1:10],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)

plot(spy.test, type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$SPX ARMA(1,1) 50-Day Forecast")
lines(seq(1,50),spy1.1f$f,type = "l", lty = 2)
legend(2, 1800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
```
#### So the best model we see by ASE is still the ARIMA(3,1,2) which is good because we know from background knowledge that open interest should not be stationary

#Now we look at Rolling window ASE for both long and short term time horizons
```{r include=FALSE}
spy = oi$SPX.Open.Interest

vsRMSE41 = roll.win.rmse.wge(spy,horizon = 5, d = 1, phi = spy41$phi, theta = spy41$theta)
vsRMSE32 = roll.win.rmse.wge(spy,horizon = 5, d = 1, phi = spy32$phi, theta = spy32$theta)
vsRMSE11 = roll.win.rmse.wge(spy,horizon = 5, d = 1, phi = spy11$phi, theta = spy11$theta)

vsRMSE1.2 = roll.win.rmse.wge(spy,horizon = 5, phi = spy1.2$phi, theta = spy1.2$theta)
vsRMSE1.1 = roll.win.rmse.wge(spy,horizon = 5, phi = spy1.1$phi, theta = spy1.1$theta)
vsRMSE2.0 = roll.win.rmse.wge(spy,horizon = 5, phi = spy2.0$phi, theta = 0)

sRMSE41 = roll.win.rmse.wge(spy,horizon = 10, d = 1, phi = spy41$phi, theta = spy41$theta)
sRMSE32 = roll.win.rmse.wge(spy,horizon = 10, d = 1, phi = spy32$phi, theta = spy32$theta)
sRMSE11 = roll.win.rmse.wge(spy,horizon = 10, d = 1, phi = spy11$phi, theta = spy11$theta)

sRMSE1.2 = roll.win.rmse.wge(spy,horizon = 10, phi = spy1.2$phi, theta = spy1.2$theta)
sRMSE1.1 = roll.win.rmse.wge(spy,horizon = 10, phi = spy1.1$phi, theta = spy1.1$theta)
sRMSE2.0 = roll.win.rmse.wge(spy,horizon = 10, phi = spy2.0$phi, theta = 0)


lRMSE41 = roll.win.rmse.wge(spy,horizon = 50, d = 1, phi = spy41$phi, theta = spy41$theta)
lRMSE32 = roll.win.rmse.wge(spy,horizon = 50, d = 1, phi = spy32$phi, theta = spy32$theta)
lRMSE11 = roll.win.rmse.wge(spy,horizon = 50, d = 1, phi = spy11$phi, theta = spy11$theta)

lRMSE1.2 = roll.win.rmse.wge(spy,horizon = 50, phi = spy1.2$phi, theta = spy1.2$theta)
lRMSE1.1 = roll.win.rmse.wge(spy,horizon = 50, phi = spy1.1$phi, theta = spy1.1$theta)
lRMSE2.0 = roll.win.rmse.wge(spy,horizon = 50, phi = spy2.0$phi, theta = 0)
```
```{r}
vsRMSE11$rwRMSE
vsRMSE41$rwRMSE
vsRMSE32$rwRMSE

vsRMSE1.1$rwRMSE
vsRMSE1.2$rwRMSE
vsRMSE2.0$rwRMSE

sRMSE11$rwRMSE
sRMSE41$rwRMSE
sRMSE32$rwRMSE

sRMSE1.1$rwRMSE
sRMSE1.2$rwRMSE
sRMSE2.0$rwRMSE

lRMSE11$rwRMSE
lRMSE41$rwRMSE
lRMSE32$rwRMSE

lRMSE1.1$rwRMSE
lRMSE1.2$rwRMSE
lRMSE2.0$rwRMSE
```
```{r}
lRMSE32$rwRMSE
lRMSE11$rwRMSE
lRMSE1.2$rwRMSE
```
### Check ljung box for stationary models

```{r}
plotts.sample.wge(spy1.1$res, arlimits = T)
ljungbox1.1 = ljung.wge(spy1.1$res, p = 1, q = 1)
ljungbox1.1.48 = ljung.wge(spy1.1$res, p = 1, q = 1, K = 48)

plotts.sample.wge(spy1.2$res, arlimits = T)
ljungbox1.2 = ljung.wge(spy1.2$res, p = 1, q = 2)
ljungbox1.2.48 = ljung.wge(spy1.2$res, p = 1, q = 2, K = 48)

plotts.sample.wge(spy2.0$res, arlimits = T)
ljungbox2.0 = ljung.wge(spy2.0$res, p = 2)
ljungbox2.0.48 = ljung.wge(spy2.0$res, p = 2, K = 48)
```
```{r}
ljungbox1.1$pval
ljungbox1.1.48$pval
ljungbox1.2$pval
ljungbox1.2.48$pval
ljungbox2.0$pval
ljungbox2.0.48$pval
```

### Seems like Stationary ARMA(1,2) model performs the best when looking at rolling window RMSE, also, it is not far off when looking at traditional ASE

#### Now Apple
```{r}
aapl.train = oi.train$AAPL.Open.Interest
plotts.sample.wge(aapl.train)
adf.test(aapl.train)
par(mfrow = c(1,1))
plotts.wge(aapl.train)
acf(aapl.train, lag.max = 25)
parzen.wge(aapl.train)
```
### Intitioal Thoughts
#### Seems stationary and has constant variance
#### Seems like it has damping ACF, could be a little damped sinusoidal
#### Frequency plot has peak at 0 and has small peak at 0.2
#### Lets check non-stationary models
```{r}
aapl.d1 = artrans.wge(aapl.train, phi.tr = 1)
plotts.sample.wge(aapl.d1, arlimits = T)
#aic5.wge(aapl.d1, p = 0:10, q = 0:10)
#aic5.wge(aapl.d1, p = 0:10, q = 0:10, type = "bic")
```
#### I suspect some seasonality
```{r}
factor.wge(phi = c(rep(0,4),1))
est.ar.wge(aapl.d1, p = 7, method = 'mle')
```
### Overfitting does not let us conclude that there is any seasonality for s = 5. We move on to fitting models

###We will also fit some stationary models
```{r}
aic5.wge(aapl.train, p = 0:10, q = 0:10)
aic5.wge(aapl.train, p = 0:10, q = 0:10, type = "bic")
```

#### Differencing seems to take out much of the sample correlations
#### For non-stationary models, after checking AIC and BIC, the 4 models that I will fit are ARIMA(5,1,6), ARIMA(9,1,5), ARIMA(1,1,1) and ARIMA(0,1,3)
#### For Stationary models, the models i will check are ARMA(6,8), ARMA(4,7), AR(5), AR(4)
```{r}
aapl516 = est.arma.wge(aapl.d1, p = 5, q = 6)
aapl915 = est.arma.wge(aapl.d1, p = 9, q = 5)
aapl111 = est.arma.wge(aapl.d1, p = 1, q = 1)
aapl013 = est.arma.wge(aapl.d1, p = 0, q = 3)
aapl68 = est.arma.wge(aapl.train, p = 6, q = 8)
aapl47 = est.arma.wge(aapl.train, p = 4, q = 7 )
aapl50 = est.ar.wge(aapl.train, p = 5, method = 'burg')
aapl40 = est.ar.wge(aapl.train, p = 4, method = 'burg')
```
```{r}
aapl.test = oi.test$AAPL.Open.Interest

aapl516f = fore.arima.wge(aapl.train, phi = aapl516$phi, theta = aapl516$theta, d = 1, n.ahead = 50)
aapl915f = fore.arima.wge(aapl.train, phi = aapl915$phi, theta = aapl915$theta, d = 1, n.ahead = 50)
aapl111f = fore.arima.wge(aapl.train, phi = aapl111$phi, theta = aapl111$theta, d = 1, n.ahead = 50)
aapl013f = fore.arima.wge(aapl.train, phi = 0, theta = aapl013$theta, d = 1, n.ahead = 50)
aapl68f = fore.arma.wge(aapl.train, phi = aapl68$phi, theta = aapl68$theta, n.ahead = 50)
aapl47f = fore.arma.wge(aapl.train, phi = aapl47$phi, theta = aapl47$theta, n.ahead = 50)
aapl50f = fore.arma.wge(aapl.train, phi = aapl50$phi, theta = 0, n.ahead = 50)
aapl40f = fore.arma.wge(aapl.train, phi = aapl40$phi, theta = 0, n.ahead = 50)

aapl516ASE_5 = mean((aapl516f$f[1:5]-aapl.test[1:5])^2)
aapl915ASE_5 = mean((aapl915f$f[1:5]-aapl.test[1:5])^2)
aapl111ASE_5 = mean((aapl111f$f[1:5]-aapl.test[1:5])^2)
aapl013ASE_5 = mean((aapl013f$f[1:5]-aapl.test[1:5])^2)
aapl68ASE_5 = mean((aapl68f$f[1:5]-aapl.test[1:5])^2)
aapl47ASE_5 = mean((aapl47f$f[1:5]-aapl.test[1:5])^2)
aapl50ASE_5 = mean((aapl50f$f[1:5]-aapl.test[1:5])^2)
aapl40ASE_5 = mean((aapl40f$f[1:5]-aapl.test[1:5])^2)

aapl516ASE_10 = mean((aapl516f$f[1:10]-aapl.test[1:10])^2)
aapl915ASE_10 = mean((aapl915f$f[1:10]-aapl.test[1:10])^2)
aapl111ASE_10 = mean((aapl111f$f[1:10]-aapl.test[1:10])^2)
aapl013ASE_10 = mean((aapl013f$f[1:10]-aapl.test[1:10])^2)
aapl68ASE_10 = mean((aapl68f$f[1:10]-aapl.test[1:10])^2)
aapl47ASE_10 = mean((aapl47f$f[1:10]-aapl.test[1:10])^2)
aapl50ASE_10 = mean((aapl50f$f[1:10]-aapl.test[1:10])^2)
aapl40ASE_10 = mean((aapl40f$f[1:10]-aapl.test[1:10])^2)

aapl516ASE = mean((aapl516f$f-aapl.test)^2)
aapl915ASE = mean((aapl915f$f-aapl.test)^2)
aapl111ASE = mean((aapl111f$f-aapl.test)^2)
aapl013ASE = mean((aapl013f$f-aapl.test)^2)
aapl68ASE = mean((aapl68f$f-aapl.test)^2)
aapl47ASE = mean((aapl47f$f-aapl.test)^2)
aapl50ASE = mean((aapl50f$f-aapl.test)^2)
aapl40ASE = mean((aapl40f$f-aapl.test)^2)
```
```{r}
plot(aapl.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$AAPL ARMA(4, 7) 5-Day Forecast")
lines(seq(1,5),aapl47f$f[1:5],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)

plot(aapl.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$AAPL ARMA(4, 7) 10-Day Forecast")
lines(seq(1,10),aapl47f$f[1:10],col = 'blue', lty = 2)
legend(2, 1800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)

plot(aapl.test, type = "l",ylim = c(1000000, 6000000)  ,ylab = "Open Interest", xlab = "Days Ahead", main = "$AAPL ARMA(4, 7) 50-Day Forecast")
lines(seq(1,50),aapl47f$f,col = 'blue', lty = 2)
legend(2, 6000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
```

```{r}
aapl516ASE_5
aapl915ASE_5
aapl111ASE_5
aapl013ASE_5
aapl68ASE_5
aapl47ASE_5
aapl50ASE_5
aapl40ASE_5
```

```{r}
aapl516ASE_10
aapl915ASE_10
aapl111ASE_10
aapl013ASE_10
aapl68ASE_10
aapl47ASE_10
aapl50ASE_10
aapl40ASE_10
```
```{r}
aapl516ASE
aapl915ASE
aapl111ASE
aapl013ASE
aapl68ASE
aapl47ASE
aapl50ASE
aapl40ASE
```
#Top 5 performing models by ASE were the ARIMA(9,1,5), ARMA(6,8), ARMA(4,7), AR(5), AR(4)

#Now we look at Rolling window ASE for both long and short term time horizons at the top 5 performing models
```{r include=FALSE}
aapl = oi$AAPL.Open.Interest

vsRMSE516 = roll.win.rmse.wge(aapl,horizon = 5, d = 1, phi = aapl516$phi, theta = aapl516$theta)
vsRMSE915 = roll.win.rmse.wge(aapl,horizon = 5, d = 1, phi = aapl915$phi, theta = aapl915$theta)
vsRMSE111 = roll.win.rmse.wge(aapl,horizon = 5, d = 1, phi = aapl111$phi, theta = aapl111$theta)
vsRMSE68 = roll.win.rmse.wge(aapl,horizon = 5, phi = aapl68$phi, theta = aapl68$theta)
vsRMSE47 = roll.win.rmse.wge(aapl,horizon = 5, phi = aapl47$phi, theta = aapl47$theta)
vsRMSE50 = roll.win.rmse.wge(aapl,horizon = 5, phi = aapl50$phi)

sRMSE516 = roll.win.rmse.wge(aapl,horizon = 10, d = 1, phi = aapl516$phi, theta = aapl516$theta)
sRMSE915 = roll.win.rmse.wge(aapl,horizon = 10, d = 1, phi = aapl915$phi, theta = aapl915$theta)
sRMSE111 = roll.win.rmse.wge(aapl,horizon = 10, d = 1, phi = aapl111$phi, theta = aapl111$theta)
sRMSE68 = roll.win.rmse.wge(aapl,horizon = 10, phi = aapl68$phi, theta = aapl68$theta)
sRMSE47 = roll.win.rmse.wge(aapl,horizon = 10, phi = aapl47$phi, theta = aapl47$theta)
sRMSE50 = roll.win.rmse.wge(aapl,horizon = 10, phi = aapl50$phi)

lRMSE516 = roll.win.rmse.wge(aapl,horizon = 50, d = 1, phi = aapl516$phi, theta = aapl516$theta)
lRMSE915 = roll.win.rmse.wge(aapl,horizon = 50, d = 1, phi = aapl915$phi, theta = aapl915$theta)
lRMSE111 = roll.win.rmse.wge(aapl,horizon = 50, d = 1, phi = aapl111$phi, theta = aapl111$theta)
lRMSE68 = roll.win.rmse.wge(aapl,horizon = 50, phi = aapl68$phi, theta = aapl68$theta)
lRMSE47 = roll.win.rmse.wge(aapl,horizon = 50, phi = aapl47$phi, theta = aapl47$theta)
lRMSE50 = roll.win.rmse.wge(aapl,horizon = 50, phi = aapl50$phi)

```

```{r}
vsRMSE516$rwRMSE
vsRMSE915$rwRMSE
vsRMSE111$rwRMSE
vsRMSE68$rwRMSE
vsRMSE47$rwRMSE
vsRMSE50$rwRMSE

```

```{r}
sRMSE516$rwRMSE
sRMSE915$rwRMSE
sRMSE111$rwRMSE
sRMSE68$rwRMSE
sRMSE47$rwRMSE
sRMSE50$rwRMSE

```
```{r}
lRMSE516$rwRMSE
lRMSE915$rwRMSE
lRMSE111$rwRMSE
lRMSE68$rwRMSE
lRMSE47$rwRMSE
lRMSE50$rwRMSE

```
#AR(5) has the best score using rolling windown RMSE in all 3 windows
#AR(4,7) has among the top scores for all 6 measures except for 10 day ASE
```{r}
ljungbox516 = ljung.wge(aapl516$res, p = 5, q = 6)
ljungbox516.48 = ljung.wge(aapl516$res, p = 5, q = 6, K = 48)

ljungbox915 = ljung.wge(aapl915$res, p = 9, q = 5)
ljungbox915.48 = ljung.wge(aapl915$res, p = 9, q = 5, K = 48)

ljungbox111 = ljung.wge(aapl111$res, p = 1, q = 1)
ljungbox111.48 = ljung.wge(aapl111$res, p = 1, q = 1, K = 48)

ljungbox68 = ljung.wge(aapl68$res, p = 6, q = 8)
ljungbox68.48 = ljung.wge(aapl68$res, p = 6, q = 8, K = 48)

ljungbox47 = ljung.wge(aapl47$res, p = 4, q = 7)
ljungbox47.48 = ljung.wge(aapl47$res, p = 4, q = 7, K = 48)

ljungbox50 = ljung.wge(aapl50$res, p = 5)
ljungbox50.48 = ljung.wge(aapl50$res, p = 5, K = 48)
```
```{r}
ljungbox516$pval
ljungbox516.48$pval

ljungbox915$pval
ljungbox915.48$pval

ljungbox111$pval
ljungbox111.48$pval

ljungbox68$pval
ljungbox68.48$pval

ljungbox47$pval
ljungbox47.48$pval

ljungbox50$pval
ljungbox50.48$pval
```

# AR(4,7) was the best

##MLP - SPY
```{r}
ts.spy.train = ts(spy.train)
ts.spy.test = ts(spy.test)
```

#Create 4 candidate NN models to evaluate
```{r}
spyfit1 = mlp(ts.spy.train)
spyfit1
plot(spyfit1)
```
```{r}
spyfit2 = mlp(ts.spy.train, hd.auto.type = 'cv')
spyfit2
plot(spyfit2)
```
```{r}
spyfit3 = mlp(ts.spy.train, lags = 1)
spyfit3
plot(spyfit3)
```
```{r}
spyfit4 = mlp(ts.spy.train, difforder = 1)
spyfit4
plot(spyfit4)
```

```{r}
f1 = forecast(spyfit1, h = 50)

plot(ts.spy.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,5),f1$mean[1:5],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f1.ASE5 = mean((ts.spy.test[1:5]-f1$mean[1:5])^2)

plot(ts.spy.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f1$mean[1:10],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f1.ASE10 = mean((ts.spy.test[1:10]-f1$mean[1:10])^2)

plot(ts.spy.test, type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f1$mean,type = "l", lty = 2)
legend(1, 1800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f1.ASE50 = mean((ts.spy.test-f1$mean[1:50])^2)

```

```{r}
f2 = forecast(spyfit2, h = 50)

plot(ts.spy.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,5),f2$mean[1:5],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f2.ASE5 = mean((ts.spy.test[1:5]-f2$mean[1:5])^2)

plot(ts.spy.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f2$mean[1:10],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f2.ASE10 = mean((ts.spy.test[1:10]-f2$mean[1:10])^2)

plot(ts.spy.test, type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f2$mean,type = "l", lty = 2)
legend(1, 1800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f2.ASE50 = mean((ts.spy.test-f2$mean[1:50])^2)
```

```{r}
f3 = forecast(spyfit3, h = 50)

plot(ts.spy.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$SPX MLP 5-Day Forecast")
lines(seq(1,5),f3$mean[1:5],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f3.ASE5 = mean((ts.spy.test[1:5]-f3$mean[1:5])^2)

plot(ts.spy.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$SPX MLP 10-Day Forecast")
lines(seq(1,10),f3$mean[1:10],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f3.ASE10 = mean((ts.spy.test[1:10]-f3$mean[1:10])^2)

plot(ts.spy.test, type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$SPX MLP 50-Day Forecast")
lines(seq(1,50),f3$mean, col = "blue", lty = 2)
legend(1, 1800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f3.ASE50 = mean((ts.spy.test-f3$mean[1:50])^2)
```

```{r}
f4 = forecast(spyfit4, h = 50)

plot(ts.spy.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,5),f4$mean[1:5],col = 'blue', lty = 2)
legend(6, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f4.ASE5 = mean((ts.spy.test[1:5]-f4$mean[1:5])^2)

plot(ts.spy.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f4$mean[1:10],col = 'blue', lty = 2)
legend(2, 1500000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f4.ASE10 = mean((ts.spy.test[1:10]-f4$mean[1:10])^2)

plot(ts.spy.test, type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f4$mean,type = "l", lty = 2)
legend(1, 1800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f4.ASE50 = mean((ts.spy.test-f4$mean[1:50])^2)
```
```{r}
f1.ASE5
f2.ASE5
f3.ASE5
f4.ASE5

f1.ASE10
f2.ASE10
f3.ASE10
f4.ASE10

f1.ASE50
f2.ASE50
f3.ASE50
f4.ASE50
```
```{r}
ts.spy = ts(oi$SPX.Open.Interest)

vsRWRMSE1 = roll.win.rmse.nn.wge(ts.spy, horizon = 5, spyfit1)
vsRWRMSE2 = roll.win.rmse.nn.wge(ts.spy, horizon = 5, spyfit2)
vsRWRMSE3 = roll.win.rmse.nn.wge(ts.spy, horizon = 5, spyfit3)
vsRWRMSE4 = roll.win.rmse.nn.wge(ts.spy, horizon = 5, spyfit4)

sRWRMSE1 = roll.win.rmse.nn.wge(ts.spy, horizon = 10, spyfit1)
sRWRMSE2 = roll.win.rmse.nn.wge(ts.spy, horizon = 10, spyfit2)
sRWRMSE3 = roll.win.rmse.nn.wge(ts.spy, horizon = 10, spyfit3)
sRWRMSE4 = roll.win.rmse.nn.wge(ts.spy, horizon = 10, spyfit4)

lRWRMSE1 = roll.win.rmse.nn.wge(ts.spy, horizon = 50, spyfit1)
lRWRMSE2 = roll.win.rmse.nn.wge(ts.spy, horizon = 50, spyfit2)
lRWRMSE3 = roll.win.rmse.nn.wge(ts.spy, horizon = 50, spyfit3)
lRWRMSE4 = roll.win.rmse.nn.wge(ts.spy, horizon = 50, spyfit4)
```
```{r}
vsRWRMSE1$rwRMSE 
vsRWRMSE2$rwRMSE 
vsRWRMSE3$rwRMSE 
vsRWRMSE4$rwRMSE 
```

```{r}
sRWRMSE1$rwRMSE 
sRWRMSE2$rwRMSE 
sRWRMSE3$rwRMSE 
sRWRMSE4$rwRMSE 
```


```{r}
lRWRMSE1$rwRMSE 
lRWRMSE2$rwRMSE 
lRWRMSE3$rwRMSE 
lRWRMSE4$rwRMSE 
```
## Seems like fit 2 and fit 3 have the best short and long term rolling window RMSE's of all of our spy models. 
## fit 3 seems the best
#Lets incorporate put/call ratio and see if we can improve our performance for our MLP models
```{r}
oi.train2 = oi[15:384,]
oi.test2 = oi[385:434,]

spy.oi.train = ts(as.numeric(oi.train2$SPX.Open.Interest))
spy.oi.test = ts(as.numeric(oi.test2$SPX.Open.Interest))
spy.pc = ts(as.numeric(oi$SPX.Put_Call_Ratio[15:434]))
spy.pc.df = data.frame(spy_pc_ratio = spy.pc)
plotts.sample.wge(spy.pc)
```

```{r}
spyfit_pc1 = mlp(spy.oi.train, xreg = spy.pc.df)
plot(spyfit_pc1)
```

```{r}
spyfit_pc2 = mlp(spy.oi.train, xreg = spy.pc.df, hd.auto.type = 'cv')
plot(spyfit_pc2)
```
```{r}
spyfit_pc3 = mlp(spy.oi.train, xreg = spy.pc.df, lags = 1)
plot(spyfit_pc2)
```

```{r}
f5 = forecast(spyfit_pc1, h = 50, xreg = spy.pc.df)

plot(spy.oi.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f5$mean[1:5],col = 'blue', lty = 2)
legend(3, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f5.ASE5 = mean((spy.oi.test[1:5]-f5$mean[1:5])^2)

plot(spy.oi.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f5$mean[1:10],col = 'blue', lty = 2)
legend(3, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f5.ASE10 = mean((spy.oi.test[1:10]-f5$mean[1:10])^2)

plot(spy.oi.test, type = "l", ylim = c(500000, 2000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f5$mean,type = "l", lty = 2)
legend(2, 2000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f5.ASE50 = mean((spy.oi.test-f5$mean[1:50])^2)
```

```{r}
f6 = forecast(spyfit_pc2, h = 50, xreg = spy.pc.df)

plot(spy.oi.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f6$mean[1:5],col = 'blue', lty = 2)
legend(3, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f6.ASE5 = mean((spy.oi.test[1:5]-f6$mean[1:5])^2)

plot(spy.oi.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f6$mean[1:10],col = 'blue', lty = 2)
legend(3, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f6.ASE10 = mean((spy.oi.test[1:10]-f6$mean[1:10])^2)

plot(spy.oi.test, type = "l", ylim = c(500000, 2000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f6$mean,type = "l", lty = 2)
legend(2, 2000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f6.ASE50 = mean((spy.oi.test-f6$mean[1:50])^2)
```

```{r}
f7 = forecast(spyfit_pc3, h = 50, xreg = spy.pc.df)

plot(spy.oi.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f7$mean[1:5],col = 'blue', lty = 2)
legend(3, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f7.ASE5 = mean((spy.oi.test[1:5]-f7$mean[1:5])^2)

plot(spy.oi.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f7$mean[1:10],col = 'blue', lty = 2)
legend(3, 1400000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f7.ASE10 = mean((spy.oi.test[1:10]-f7$mean[1:10])^2)

plot(spy.oi.test, type = "l", ylim = c(500000, 2000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f7$mean,type = "l", lty = 2)
legend(2, 2000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f7.ASE50 = mean((spy.oi.test-f7$mean[1:50])^2)
```

```{r}
f5.ASE5
f6.ASE5
f7.ASE5

f5.ASE10
f6.ASE10
f7.ASE10

f5.ASE50
f6.ASE50
f7.ASE50
```
## fit 7 is the best multivariate MLP model


##MLP - AAPL
```{r}
ts.aapl.train = ts(aapl.train)
ts.aapl.test = ts(aapl.test)
```
#Create 4 candidate NN models to evaluate
```{r}
aaplfit1 = mlp(ts.aapl.train)
aaplfit1
plot(aaplfit1)
```
```{r}
aaplfit2 = mlp(ts.aapl.train, hd.auto.type = 'cv')
aaplfit2
plot(aaplfit2)
```
```{r}
aaplfit3 = mlp(ts.aapl.train, lags = 1)
aaplfit3
plot(aaplfit3)
```
```{r}
aaplfit4 = mlp(ts.aapl.train, difforder = 1)
aaplfit4
plot(aaplfit4)
```

```{r}
f1 = forecast(aaplfit1, h = 50)

plot(ts.aapl.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$AAPL MLP 5-Day Forecast")
lines(seq(1,5),f1$mean[1:5],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f1.ASE5 = mean((ts.aapl.test[1:5]-f1$mean[1:5])^2)

plot(ts.aapl.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "$AAPL MLP 10-Day Forecast")
lines(seq(1,10),f1$mean[1:10],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f1.ASE10 = mean((ts.aapl.test[1:10]-f1$mean[1:10])^2)

plot(ts.aapl.test, type = "l", ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "$AAPL MLP 50-Day Forecast")
lines(seq(1,50),f1$mean, col = 'blue', lty = 2)
legend(1, 5800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f1.ASE50 = mean((ts.aapl.test-f1$mean[1:50])^2)
```

```{r}
f2 = forecast(aaplfit2, h = 50)

plot(ts.aapl.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f2$mean[1:5],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f2.ASE5 = mean((ts.aapl.test[1:5]-f2$mean[1:5])^2)

plot(ts.aapl.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f2$mean[1:10],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f2.ASE10 = mean((ts.aapl.test[1:10]-f2$mean[1:10])^2)

plot(ts.aapl.test, type = "l", ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f2$mean,type = "l", lty = 2)
legend(1, 5800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f2.ASE50 = mean((ts.aapl.test-f2$mean[1:50])^2)
```

```{r}
f3 = forecast(aaplfit3, h = 50)

plot(ts.aapl.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f3$mean[1:5],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f3.ASE5 = mean((ts.aapl.test[1:5]-f3$mean[1:5])^2)

plot(ts.aapl.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f3$mean[1:10],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f3.ASE10 = mean((ts.aapl.test[1:10]-f3$mean[1:10])^2)

plot(ts.aapl.test, type = "l", ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f3$mean,type = "l", lty = 2)
legend(1, 5800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f3.ASE50 = mean((ts.aapl.test-f3$mean[1:50])^2)
```

```{r}
f4 = forecast(aaplfit4, h = 50)

plot(ts.aapl.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f4$mean[1:5],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f4.ASE5 = mean((ts.aapl.test[1:5]-f4$mean[1:5])^2)

plot(ts.aapl.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f4$mean[1:10],col = 'blue', lty = 2)
legend(1, 1700000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f4.ASE10 = mean((ts.aapl.test[1:10]-f4$mean[1:10])^2)

plot(ts.aapl.test, type = "l", ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f4$mean,type = "l", lty = 2)
legend(1, 5800000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f4.ASE50 = mean((ts.aapl.test-f4$mean[1:50])^2)
```
```{r}
f1.ASE5
f2.ASE5
f3.ASE5
f4.ASE5
```
```{r}
f1.ASE10
f2.ASE10
f3.ASE10
f4.ASE10
```
```{r}
f1.ASE50
f2.ASE50
f3.ASE50
f4.ASE50
```

#Based on ASE, none of the NN models outperform the other models for AAPL open interest data

#Lets incorporate put/call ratio and see if we can improve our performance for our MLP models
```{r}
oi.train3 = oi[16:384,]

aapl.oi.train = ts(as.numeric(oi.train3$AAPL.Open.Interest))
aapl.oi.test = ts(as.numeric(oi.test2$AAPL.Open.Interest))
aapl.pc =  ts(as.numeric(oi$AAPL.Put_Call_Ratio[16:434]))
aapl.pc.df = data.frame(aapl_pc_ratio = aapl.pc)
plotts.sample.wge(aapl.pc)
```
```{r}
aaplfit_pc1 = mlp(aapl.oi.train, xreg = aapl.pc.df)
aaplfit_pc1
plot(aaplfit_pc1)
```

```{r}
aaplfit_pc2 = mlp(aapl.oi.train, xreg = aapl.pc.df, hd.auto.type = 'cv')
aaplfit_pc2
plot(aaplfit_pc2)
```
```{r}
aaplfit_pc3 = mlp(aapl.oi.train, xreg = aapl.pc.df, lags = 1)
aaplfit_pc3
plot(aaplfit_pc3)
```

```{r}
f5 = forecast(aaplfit_pc1, h = 50, xreg = aapl.pc.df)

plot(aapl.oi.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f5$mean[1:5],col = 'blue', lty = 2)
legend(3, 1600000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f5.ASE5 = mean((aapl.oi.test[1:5]-f5$mean[1:5])^2)

plot(aapl.oi.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f5$mean[1:10],col = 'blue', lty = 2)
legend(3, 1600000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f5.ASE10 = mean((aapl.oi.test[1:10]-f5$mean[1:10])^2)

plot(aapl.oi.test, type = "l",ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f5$mean,type = "l", lty = 2)
legend(2, 6000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f5.ASE50 = mean((aapl.oi.test-f5$mean[1:50])^2)
```
```{r}
f6 = forecast(aaplfit_pc2, h = 50, xreg = aapl.pc.df)

plot(aapl.oi.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f6$mean[1:5],col = 'blue', lty = 2)
legend(3, 1600000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f6.ASE5 = mean((aapl.oi.test[1:5]-f6$mean[1:5])^2)

plot(aapl.oi.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f6$mean[1:10],col = 'blue', lty = 2)
legend(3, 1600000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f6.ASE10 = mean((aapl.oi.test[1:10]-f6$mean[1:10])^2)

plot(aapl.oi.test, type = "l",ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f6$mean,type = "l", lty = 2)
legend(2, 6000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f6.ASE50 = mean((aapl.oi.test-f6$mean[1:50])^2)
```

```{r}
f7 = forecast(aaplfit_pc3, h = 50, xreg = aapl.pc.df)

plot(aapl.oi.test[1:5], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "5-Day Forecast")
lines(seq(1,5),f7$mean[1:5],col = 'blue', lty = 2)
legend(3, 1600000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f7.ASE5 = mean((aapl.oi.test[1:5]-f7$mean[1:5])^2)

plot(aapl.oi.test[1:10], type = "l", ylab = "Open Interest", xlab = "Days Ahead", main = "10-Day Forecast")
lines(seq(1,10),f7$mean[1:10],col = 'blue', lty = 2)
legend(3, 1600000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f7.ASE10 = mean((aapl.oi.test[1:10]-f7$mean[1:10])^2)

plot(aapl.oi.test, type = "l",ylim = c(500000, 6000000), ylab = "Open Interest", xlab = "Days Ahead", main = "50-Day Forecast")
lines(seq(1,50),f7$mean,type = "l", lty = 2)
legend(2, 6000000, legend = c("Actual Open Interest", "Forecasted Open Interest"), lty = 1:2)
f7.ASE50 = mean((aapl.oi.test-f7$mean[1:50])^2)
```
```{r}
f5.ASE5
f6.ASE5
f7.ASE5
```
```{r}
f5.ASE10
f6.ASE10
f7.ASE10
```
```{r}
f5.ASE50
f6.ASE50
f7.ASE50
```
#Lets look at some rolling window RMSE
```{r}
ts.aapl = ts(oi$AAPL.Open.Interest)

vsRWRMSE1 = roll.win.rmse.nn.wge(ts.aapl, horizon = 5, aaplfit1)
vsRWRMSE2 = roll.win.rmse.nn.wge(ts.aapl, horizon = 5, aaplfit2)
vsRWRMSE3 = roll.win.rmse.nn.wge(ts.aapl, horizon = 5, aaplfit3)
vsRWRMSE4 = roll.win.rmse.nn.wge(ts.aapl, horizon = 5, aaplfit4)

sRWRMSE1 = roll.win.rmse.nn.wge(ts.aapl, horizon = 10, aaplfit1)
sRWRMSE2 = roll.win.rmse.nn.wge(ts.aapl, horizon = 10, aaplfit2)
sRWRMSE3 = roll.win.rmse.nn.wge(ts.aapl, horizon = 10, aaplfit3)
sRWRMSE4 = roll.win.rmse.nn.wge(ts.aapl, horizon = 10, aaplfit4)

lRWRMSE1 = roll.win.rmse.nn.wge(ts.aapl, horizon = 50, aaplfit1)
lRWRMSE2 = roll.win.rmse.nn.wge(ts.aapl, horizon = 50, aaplfit2)
lRWRMSE3 = roll.win.rmse.nn.wge(ts.aapl, horizon = 50, aaplfit3)
lRWRMSE4 = roll.win.rmse.nn.wge(ts.aapl, horizon = 50, aaplfit4)
```
```{r}
vsRWRMSE1$rwRMSE 
vsRWRMSE2$rwRMSE 
vsRWRMSE3$rwRMSE 
vsRWRMSE4$rwRMSE 
```

```{r}
sRWRMSE1$rwRMSE 
sRWRMSE2$rwRMSE 
sRWRMSE3$rwRMSE 
sRWRMSE4$rwRMSE 
```


```{r}
lRWRMSE1$rwRMSE 
lRWRMSE2$rwRMSE 
lRWRMSE3$rwRMSE 
lRWRMSE4$rwRMSE 
```
## Seems like fit 2 and fit 3 have the best short and long term rolling window RMSE's of all of our aapl models, but no improvement upon the other models



